Adaptive Algorithms Employing Continuous Linear Functionals

### 2018-08-03 AutoAlgorithmLinearFunctionalDataVerC.tex
fixed a comment in the intro

The computational cost of an algorithm $A \in \ca(\ch)$ for $f \in \ch$ and error tolerance $\varepsilon$ is denoted $\cost(A,f,\varepsilon)$, and is defined as the number of linear functional values required to produce $A(f,\varepsilon)$.  By overloading the notation, we define for arbitrary algorithms $A \in \ca(\ch)$, 
\begin{equation*}
\cost(A,\ch,\varepsilon) : = \sup \{\cost(A,f,\varepsilon) : f \in \ch \} \qquad \forall \varepsilon > 0.
\end{equation*}
For unbounded sets, $\ch$, this cost may be infinite.  Therefore, it is also helpful to define the cost for input functions in $\ch \cap \cb_{\rho}$, where $\cb_{\rho} : = \{ f \in \cf : \norm[\cf]{f} \le \rho \}$ is the ball of radius $\rho$:
\begin{equation*}
\cost(A,\ch,\varepsilon,\rho) : = \sup \{\cost(A,f,\varepsilon) : f \in \ch \cap \cb_{\rho} \} \qquad \forall \rho > 0, \ \varepsilon > 0.
\end{equation*}
Note that $\cost(A,\ch,\varepsilon,\rho)$ is no less than---but possibly greater than---$\cost(A,\ch \cap \cb_{\rho},\varepsilon)$.  In the former case, the algorithm is unaware  that the input function has norm no greater than $\rho$.  
Finally, we define the complexity of the problem as computational cost of the best algorithm:
\begin{gather*}
\comp(\ca(\ch),\varepsilon) := \min_{A \in \ca(\ch)} \cost(A, \ch, \varepsilon), \\
\comp(\ca(\ch),\varepsilon,\rho) := \min_{A \in \ca(\ch)} \cost(A, \ch, \varepsilon, \rho).
\end{gather*}

>>>>

The computational cost of an algorithm $A \in \ca(\ch)$ for $f \in \ch$ and error tolerance $\varepsilon$ is denoted $\cost(A,f,\varepsilon)$, and is defined as the number of linear functional values required to produce $A(f,\varepsilon)$.  By overloading the notation, we define for arbitrary algorithms $A \in \ca(\ch)$, 
\begin{equation*}
\cost(A,\ch,\varepsilon) : = \sup \{\cost(A,f,\varepsilon) : f \in \ch \} \qquad \forall \varepsilon > 0.
\end{equation*}
For unbounded sets, $\ch$, this cost may be infinite.  Therefore, it is also helpful to define the cost for input functions in $\ch \cap \cb_{\rho}$, where $\cb_{\rho} : = \{ f \in \cf : \norm[\cf]{f} \le \rho \}$ is the ball of radius $\rho$:
\begin{equation*}
\cost(A,\ch,\varepsilon,\rho) : = \sup \{\cost(A,f,\varepsilon) : f \in \ch \cap \cb_{\rho} \} \qquad \forall \rho > 0, \ \varepsilon > 0.
\end{equation*}
Finally, we define the complexity of the problem as computational cost of the best algorithm:
\begin{gather*}
\comp(\ca(\ch),\varepsilon) := \min_{A \in \ca(\ch)} \cost(A, \ch, \varepsilon), \\
\comp(\ca(\ch),\varepsilon,\rho) := \min_{A \in \ca(\ch)} \cost(A, \ch, \varepsilon, \rho).
\end{gather*}
Note that $\comp(\ca(\ch),\varepsilon,\rho) \ge \comp(\ca(\ch \cap \cb_{\rho}),\varepsilon)$.  In the former case, the algorithm is unaware  that the input function has norm no greater than $\rho$.
